What do incoming university students believe about open science practices in

### 2021-12-03 analysis/Manuscript.Rmd
minor formatting changes for APA

abstract: |
 BACKGROUND: Understanding students’ naive conceptions about how science works and the norms that guide scientific best practice is important so that teachers can adapt their teaching to students’ existing understandings.
 OBJECTIVE: To describe what incoming undergraduate students of psychology believe about reproducibility and open science practices in psychology.
 METHOD: International online survey with participants who were about to start their first course in psychology at a university (N = 239).
 RESULTS: When asked about how research *should* be done, most students endorsed most (but not all) of ten open science practices. When asked to estimate the proportion of published psychological studies that apply each of a set of 10 open science practices, participants' estimates tended to average near 50%. Only 18% of participants had heard of the term "replication crisis".
 CONCLUSION: Despite relatively significant media attention on the replication crisis, few incoming psychology students are familiar with the term. Incoming students nevertheless appear to be sympathetic toward most open science practices, although they may overestimate the prevalence of these practices in psychology.
 TEACHING IMPLICATIONS: Teaching materials aimed at incoming psychology students should not assume pre-existing knowledge about open science or replicability.

@@

The last decade has seen unprecedented change in methodological and reporting practices in psychology. These changes were partly precipitated by what is popularly known as the "replication crisis": The discovery that close replications of published psychological studies are often unable to replicate the original findings [@kleinInvestigatingVariationReplicability2014; @kleinManyLabsInvestigating2018]. These apparent problems with replication have led to a variety of potential solutions to make research practices more reproducible and transparent, including more frequent publication of replication studies [see @brandtReplicationRecipeWhat2014], more thorough reporting of methods and results [@wigboldusEncouragePlayingData2016], open sharing of data [see @meyerPracticalTipsEthical2018], and preregistration of data collection and analysis plans [@nosekPreregistrationRevolution2018]. These calls for more reproducible and transparent research practices have prompted the discipline to reflect on and measure researchers norms, attitudes, and practices [e.g., @baker500ScientistsLift2016; @beaudry_swinburne_2019; @harrisUseReproducibleResearch2018].

@@

knitr::kable(norm_items_wide,
             caption = "Norm and counternorm items",
             align = c('lll'))

@@

knitr::kable(practice_means,
             caption = "Means and standard deviations for norms, counternorms, and the difference between norms and counternorms, with 95% confidence intervals (in square brackets)",
             digits = 2,
             align = c('lccc'))

@@

## Norms in practice
Participants were also asked to estimate the proportion of psychology studies globally that apply each of ten practices (see Table \@ref(tab:normsinpractice)). For many of these practices, participants’ estimates were near the midpoint of 50%. This said, participants perceived some practices as being applied relatively infrequently: For example, the mean estimate of the prevalence of HARKing, preprint sharing before publication, and open data sharing were all near 30%. See Figure A in Supplemental Materials to see the distribution for each item. Participants perceived the most common practice was providing enough information in written reports to permit replication without asking any questions of the original researchers.

@@

knitr::kable(in_practice_means,
             caption = "Means, standard deviations, and 95% confidence intervals for the prevalence ratings for each research practice",
             digits = 2,
             align = c('lc'))

@@

## The replication crisis
Interestingly, only `r round(sum(df$crisis==1, na.rm = TRUE)/length(df$crisis)*100, 0)`% of participants indicated they had heard of "the replication crisis". Most (`r round(sum(df$crisis==2, na.rm = TRUE)/length(df$crisis)*100, 0)`%) indicated that they had not heard of the crisis, and `r round(sum(is.na(df$crisis))/length(df$crisis)*100, 0)`% did not respond.

@@

```{r repperchistogram, fig.cap="Histogram of participants' responses to the question: \"Imagine that a set of researchers select 100 published studies about psychology, and repeat each study again, exactly how it was described in the original report but with a new set of participants. We call repeating a study like this a \'replication study\'. At a guess, how many of these replication studies do you think would produce the same conclusions as the original studies?\" Responses provided on a visual slider from 0% to 100%."}

@@

@@

## Strengths and limitations
Despite a relatively large sample size, our results provide an imperfect picture of new psychology students’ methodological understandings. Our use of convenience samples coupled with the imprecision of polling students’ impressions at one point in time suggest that we can make only tentative generalisations to a wider population of incoming psychology students. However, collectively these results demonstrate some clear topics that might be targeted in our teaching: for example, emphasising the value of pre-prints and open data to research practice.

@@

## Conclusion and teaching implications
Overall these findings suggest that incoming psychology students have a degree of sympathy for open science norms. Nevertheless, despite significant media attention on the replication crisis, few have heard of this crisis. Similarly, students seemed to be relatively unfamiliar with responses to the replication crisis (e.g., open science practices). It is therefore important that teachers of psychology not assume pre-existing knowledge among incoming students.

@@

knitr::kable(corr,
             caption = "Correlations between norms and counternorms with the 95% confidence intervals (in square brackets) and the associated p-value",
             digits = 2,
             align = c('lccc'))

@@

```{r normsinpracticehistogram, fig.cap="Histogram of participants' prevalence ratings (%) for each of the norms in practice items. Responses provided on a visual slider from 0% to 100%."}

@@

*Figure A*

>>>>

abstract: |
 Background: Understanding students’ naive conceptions about how science works and the norms that guide scientific best practice is important so that teachers can adapt their teaching to students’ existing understandings.
 Objective: To describe what incoming undergraduate students of psychology believe about reproducibility and open science practices in psychology.
 Method: International online survey with participants who were about to start their first course in psychology at a university (N = 239).
 Results: When asked about how research *should* be done, most students endorsed most (but not all) of ten open science practices. When asked to estimate the proportion of published psychological studies that apply each of a set of 10 open science practices, participants' estimates tended to average near 50%. Only 18% of participants had heard of the term "replication crisis".
 Conclusion: Despite relatively significant media attention on the replication crisis, few incoming psychology students are familiar with the term. Incoming students nevertheless appear to be sympathetic toward most open science practices, although they may overestimate the prevalence of these practices in psychology.
 Teaching Implications: Teaching materials aimed at incoming psychology students should not assume pre-existing knowledge about open science or replicability.

@@

The last decade has seen unprecedented change in methodological and reporting practices in psychology. These changes were partly precipitated by what is popularly known as the "replication crisis": The discovery that close replications of published psychological studies are often unable to replicate the original findings [@kleinInvestigatingVariationReplicability2014; @kleinManyLabsInvestigating2018]. These apparent problems with replication have led to a variety of potential solutions to make research practices more reproducible and transparent, including more frequent publication of replication studies [see @brandtReplicationRecipeWhat2014], more thorough reporting of methods and results [@wigboldusEncouragePlayingData2016], open sharing of data [see @meyerPracticalTipsEthical2018], and preregistration of data collection and analysis plans [@nosekPreregistrationRevolution2018]. These calls for more reproducible and transparent research practices have prompted the discipline to reflect on and measure researchers' norms, attitudes, and practices [e.g., @baker500ScientistsLift2016; @beaudry_swinburne_2019; @harrisUseReproducibleResearch2018].

@@

knitr::kable(norm_items_wide,
             caption = "Norm and Counternorm Items",
             align = c('lll'))

@@

knitr::kable(practice_means,
             caption = "Means and Standard Deviations for Norms, Counternorms, and the Difference between Norms and Counternorms, with 95% Confidence Intervals (in Square Brackets)",
             digits = 2,
             align = c('lccc'))

@@

## Norms in Practice
Participants were also asked to estimate the proportion of psychology studies globally that apply each of ten practices (see Table \@ref(tab:normsinpractice)). For many of these practices, participants’ estimates were near the midpoint of 50%. This said, participants perceived some practices as being applied relatively infrequently: For example, the mean estimate of the prevalence of HARKing, preprint sharing before publication, and open data sharing were all near 30%. See Figure A in Supplemental Materials to see the distribution for each item. Participants perceived the most common practice was providing enough information in written reports to permit replication without asking any questions of the original researchers.

@@

knitr::kable(in_practice_means,
             caption = "Means, Standard Deviations, and 95% Confidence Intervals for the Prevalence Ratings for Each Research Practice",
             digits = 2,
             align = c('lc'))

@@

## The Replication Crisis
Interestingly, only `r round(sum(df$crisis==1, na.rm = TRUE)/length(df$crisis)*100, 0)`% of participants indicated they had heard of "the replication crisis". Most (`r round(sum(df$crisis==2, na.rm = TRUE)/length(df$crisis)*100, 0)`%) indicated that they had not heard of the crisis, and `r round(sum(is.na(df$crisis))/length(df$crisis)*100, 0)`% did not respond.

@@

```{r repperchistogram, fig.cap="Histogram of Participants' Estimates of the Percentage of Psychology Studies that Replicate"}

@@

*Note* responses to the question: \"Imagine that a set of researchers select 100 published studies about psychology, and repeat each study again, exactly how it was described in the original report but with a new set of participants. We call repeating a study like this a \'replication study\'. At a guess, how many of these replication studies do you think would produce the same conclusions as the original studies?\" Responses provided on a visual slider from 0% to 100%.

@@

## Strengths and Limitations
Despite a relatively large sample size, our results provide an imperfect picture of new psychology students’ methodological understandings. Our use of convenience samples coupled with the imprecision of polling students’ impressions at one point in time suggest that we can make only tentative generalisations to a wider population of incoming psychology students. However, collectively these results demonstrate some clear topics that might be targeted in our teaching: for example, emphasising the value of pre-prints and open data to research practice.

@@

## Conclusion and Teaching Implications
Overall these findings suggest that incoming psychology students have a degree of sympathy for open science norms. Nevertheless, despite significant media attention on the replication crisis, few have heard of this crisis. Similarly, students seemed to be relatively unfamiliar with responses to the replication crisis (e.g., open science practices). It is therefore important that teachers of psychology not assume pre-existing knowledge among incoming students.

@@

knitr::kable(corr,
             caption = "Correlations between Norms and Counternorms with the 95% Confidence Intervals (in Square Brackets) and the Associated p-values",
             digits = 2,
             align = c('lccc'))

@@

```{r normsinpracticehistogram, fig.cap="Histogram of Participants' Prevalence Ratings (%) for each of the Norms in Practice Items."}

@@

*Note:* Responses provided on a visual slider from 0% to 100%.
